Binary companions of red giant stars in \apogee\ \DR

### 2018-02-28 paper/1-catalog/twoface-catalog.tex
Discussion of assumption

\subsection{Orbit inference and velocity modeling}\label{sec:fitting}

@@

Here we describe the procedure we use to generate per-target posterior samplings
for the \apogee\ targets.
We execute the full procedure twice for different goals (as described in
\sectionname~\ref{sec:results}), and only here outline the key steps in the
pipeline.

For all \nstars\ \apogee\ stars with $\geq 3$ good visits (see
\sectionname~\ref{sec:data}), we use \thejoker\ to generate posterior samplings
for each star under the assumptions listed above (see
\sectionname~\ref{sec:fitting}).
We start by generating a library of \nprior\ prior samples generated under a
prior similar to that defined in \citet{Price-Whelan:2017}:
\begin{itemize}
    \item uniform or isotropic in angle parameters,
    \item uniform in log-period over the domain $[1,32768]~\textrm{day}$,
    \item a beta distribution over eccentricity with fixed parameters (\citealt{Kipping:2013}).
\end{itemize}
For the prior over the excess variance parameter, $s^2$, we initially use
a Gaussian over the transformed parameter $y = \ln s^2$ with the mean and
standard deviation $(\mu_y, \sigma_y)$ indicated where the runs are described
(see \sectionname~\ref{sec:results}).
The reference time for each star is set to the minimum visit epoch; $M_0$ then
becomes the mean anomaly at the first visit observation.
\tablename~\ref{tbl:params} contains descriptions of all parameters and priors
used.

@@

We construct a control sample of simulated data with no RV variability to assess
our false-positive rates in the selections below (see
\sectionname~\ref{sec:results}).
We randomly pick \ncontrol\ stars from the parent sample used in this work and
replace the visit velocity measurements with simulated data.
For each star $n$, we randomly sample an excess variance parameter value from
the prior, $s_n$.
For each visit $k$, we then sample a new velocity $v_{nk}$ by drawing from a
Gaussian with mean equal to the mean of the real data visit velocities,
$\bar{v}_n$, and variance equal to the sum of the visit variance (uncertainty),
$\sigma_{nk}$, and the excess variance,
\begin{equation}
    v_{nk} \sim \mathcal{N}(\bar{v}_n, \sigma_{nk}^2 + s_n^2) \quad .
\end{equation}
When we save the control data, we only store the visit uncertainty and
``forget'' the fact that the simulated data is generated with excess variance.

@@

\section{Results: companion catalogs}
\label{sec:results}

@@

@@

\todo{Return to our various assumptions and make sure that we discuss them
\emph{by name} here.}

\todo{\emph{no multiplets} punt to future work}

\todo{\emph{Kepler} evidence for coherent oscillations at the upper giant branch? companions that don't make sense}

\todo{\emph{SB1} comment that there are some companions with masses large enough that they should be evolved, and therefore should contribute to the light! where are the companions? neutron stars / BHs?}

We find that the residuals away from our best-fit two-body orbital solutions
appear close to Gaussian, indicating that the \emph{simple noise model}
assumption may be sufficient.
\figurename~\ref{fig:residuals} shows the distribution of normalized residuals,
$R_{nk}$, for each visit: the $k$ visit velocities for each $n$ star, $v_{nk}$,
minus the predicted radial velocity from the best-fitting sample returned by
\thejoker, $\hat{v}^*_{nk}$, normalized by the excess-variance-included
uncertainty, $\sigma_{nk}^* = \sqrt{\sigma_{nk}^2 + \hat{s}_{n}^2}$, where
$\hat{s}_{n}$ is computed from the excess-variance parameter of the best-fitting
sample:
\begin{equation}
    R_{nk} = \frac{v_{nk} - \hat{v}^*_{nk}}{\sqrt{\sigma_{nk}^2 +
    \hat{s}_{n}^2}} \quad . \label{eq:normresid}
\end{equation}

>>>>

\subsection{Orbit inference and velocity modeling}
\label{sec:fitting}

@@

Here we describe the procedure we use to generate per-target posterior samplings
for the \apogee\ targets.
We execute the full procedure twice for different goals (as described in
\sectionname~\ref{sec:catalogs}), and only here outline the key steps in the
pipeline.

For all \nstars\ \apogee\ stars with $\geq 3$ good visits (see
\sectionname~\ref{sec:data}), we use \thejoker\ to generate posterior samplings
for each star under the assumptions listed above (see
\sectionname~\ref{sec:fitting}).
We start by generating a library of \nprior\ prior samples generated under a
prior similar to that defined in \citet{Price-Whelan:2017}:
\begin{itemize}
    \item uniform or isotropic in angle parameters,
    \item uniform in log-period over the domain $[1,32768]~\textrm{day}$,
    \item a beta distribution over eccentricity with fixed parameters (\citealt{Kipping:2013}).
\end{itemize}
For the prior over the excess variance parameter, $s^2$, we initially use
a Gaussian over the transformed parameter $y = \ln s^2$ with the mean and
standard deviation $(\mu_y, \sigma_y)$ indicated where the runs are described
(see \sectionname~\ref{sec:catalogs}).
The reference time for each star is set to the minimum visit epoch; $M_0$ then
becomes the mean anomaly at the first visit observation.
\tablename~\ref{tbl:params} contains descriptions of all parameters and priors
used.

@@

We construct a control sample of simulated data with no RV variability to assess
our false-positive rates in the selections below (see
\sectionname~\ref{sec:catalogs}).
We randomly pick \ncontrol\ stars from the parent sample used in this work and
replace the visit velocity measurements with simulated data.
For each star $n$, we randomly sample an excess variance parameter value from
the prior, $s_n$.
For each visit $k$, we then sample a new velocity $v_{nk}$ by drawing from a
Gaussian with mean equal to the mean of the real data visit velocities,
$\bar{v}_n$, and variance equal to the sum of the visit variance (uncertainty),
$\sigma_{nk}$, and the excess variance,
\begin{equation}
    v_{nk} \sim \mathcal{N}(\bar{v}_n, \sigma_{nk}^2 + s_n^2) \quad .
\end{equation}
When we save the control data, we only store the visit uncertainty and
``forget'' the fact that the simulated data is generated with excess variance.

@@

\section{Companion catalogs}
\label{sec:catalogs}

@@

\section{Results}
\label{sec:results}

\todo{Period-logg plot - lack of short-period companions for red clump stars?}

\todo{The companions that don't make sense / can't be}

\todo{Period-eccentricity plot - tidal circularization}

\todo{Companion mass and mass-ratio distribution for stars with Ness / Martig masses}

@@

It is important to keep in mind that the companion catalogs and results
presented in this \documentname\ depend on the assumptions laid out in
\sectionname~\ref{sec:fitting}.
We have only considered radial velocity modulations from a single massive
companion---\emph{no multiplets}; This is a fundamental limitation of our search
and methodology.
However, stars with multiple companions will likely be included in our companion
catalog anyway, only with two-body orbital solutions that either don't fit the
data well or pick out the shortest period orbit.

Related to the above, we assume that all RV variations are
gravitational---\emph{Kepler}.
We see tentative evidence for coherent oscillations at the upper giant branch
(see \figurename~\ref{fig:todo}), which we presently treat as excess variance or
intrinsic jitter.
If these oscillations are indeed from asteroseismic modes, \todo{why is this
interesting?}.

We assume that one star in each two-body system overwhelmingly dominates the
luminosity and therefore spectrum of each system---\emph{SB1}.
As seen in \figurename~\ref{fig:todo}, there are some companions with minimum
masses comparable to or consistent with being larger than the masses of the
observed star.
These systems are either (a) nearly edge-on MS--RGB binaries (i.e. consistent
with our assumption), (b) SB2 systems where the \apogee\ pipeline failed to flag
the source as having broad lines or a bad fit, or (c) RGB--stellar remnant
systems with a black hole or neutron star companion.
A subset of these systems that look like they fall in category (c) are being
followed-up to obtain further RV measurements to test whether any companions are
black holes (Geha et al., in prep.).

Finally, we have assumed that the visit velocity error distribution is Gaussian,
and that the visit velocity uncertainties could be
under-estimated---\emph{simple noise model}.
We can test this assumption using posterior samples from \thejoker\ by computing
the residuals away from our best-fit two-body orbital solutions.
We find that the normalized residuals appear to be very close to Gaussian over a
large dynamic range of normalized residual values, indicating that this
assumption may be sufficient.
\figurename~\ref{fig:residuals} shows the distribution of normalized residuals,
$R_{nk}$, for each visit: the $k$ visit velocities for each $n$ star, $v_{nk}$,
minus the predicted radial velocity from the best-fitting sample returned by
\thejoker, $\hat{v}^*_{nk}$, normalized by the excess-variance-included
uncertainty, $\sigma_{nk}^* = \sqrt{\sigma_{nk}^2 + \hat{s}_{n}^2}$, where
$\hat{s}_{n}$ is computed from the excess-variance parameter of the best-fitting
sample:
\begin{equation}
    R_{nk} = \frac{v_{nk} - \hat{v}^*_{nk}}{\sqrt{\sigma_{nk}^2 +
    \hat{s}_{n}^2}} \quad . \label{eq:normresid}
\end{equation}
